Experiment 3: ratings

### 2021-06-07 analysis/exp3_analysis.Rmd
added ratingscomparison to physics support model

>>>>

## Compare Likelihood Ratings to Physics Models

```{r}
load(here("models/model_data.RData")) # mdat, all_trials_mse, all_trials_mse_r, etc.
# load(here("models/support_probability_fit_df.RData"))

#mdat %>% select(drop, target, relation, trial, support_probability) %>%
#  pivot_wider(id_cols=trial, names_from=trial, values_from=support_probability)
supp_prob <- mdat %>% select(drop, target, relation, support_probability)

trials <- adult_agg %>% select(drop, target, distractor, relation) %>%
  left_join(supp_prob, by=c("drop","target","relation")) %>%
  rename(targ_supp_prob = support_probability) %>%
  left_join(supp_prob, by=c("drop"="drop", "distractor"="target", "relation"="relation")) %>%
  rename(dist_supp_prob = support_probability) %>%
  mutate(prop_target_supp = (targ_supp_prob) / (targ_supp_prob + dist_supp_prob + 1e-5))

adult_agg %>% left_join(trials %>% select(drop, target, distractor, relation, prop_target_supp)) %>%
  ggplot(aes(x=prop_target_supp, y=prop_target_likelihood, color=relation)) + geom_point(alpha=.8) +
  xlab("Proportion Target Support in Model") +
  ylab("Luce choice of Target vs. Distractor Likelihood") +
  xlim(0,1) + ylim(0,1) + theme_classic() +
  geom_abline(slope=1, intercept=0, linetype="dashed") +
  #stat_cor(method = "pearson") 
  stat_cor(inherit.aes = F, aes(x=prop_target_supp, y=prop_target_likelihood, 
               label = paste(..rr.label.., sep = "~`,`~")))
```
